---
title: "Marine Litter Analysis Manual"
output: github_document
  # df_print: paged
---

```{r initKnitr, echo=F}
library(knitr)
library(rmarkdown)
options(max.print="90")
opts_chunk$set(echo =TRUE,
               eval=TRUE,
               cache=!TRUE,
               prompt=FALSE,
               tidy=FALSE,
               comment=NA,
               message=FALSE,
               warning=FALSE,
               results= 'markup',
               fig.margin=TRUE, 
               fig.height=5, 
               fig.width=8
)
```

\newpage

# 1. Introduction
We'd like to demonstrate how marine litter analyses are conducted.
In the analysis, ---expl

# 2. Prerequisite
## 2.1 Installation of packages
If the follwing pacakges have not been installed, please execute next commented lines first.
```{r}
#install.packages("devtools")
#install.packages("dplyr")
library(devtools)
library(dplyr)

#install_github("y-yasutomo/malia")
#calling package in order to analyze marine debris data
library(malia)
```

# 3. See Data and set up of estimation
## 3.1 Data handling 
Create data for malia package
Reading 'raw' data (at first time)  
Sighting data
```{r}
#Designate data name
#Data.name<-"おしょろ丸目視まとめC056"
#Rev.name<-"O18y1"
#Sight.hand(Data.name,Rev.name)
```
Effort data
```{r}
#Designate data name
#Data.name<-"レグ番号順 おしょろC056"
#Rev.name<-"O18y1"
#Effort.hand(Data.name,Rev.name)
```


## 3.2 Data visualization 
Survey track line
```{r}
#Designate voyage name
Vname<-"O18y1"
survey.plot(read.csv(paste(Vname,".effort.csv",sep="")))
```

## 3.3 Set up of estimation
Simple estimation using MALIA function
Reading data
```{r}
Sight.Data<-read.csv(paste(Vname,".debris.csv",sep=""))
Effort.Data<-read.csv(paste(Vname,".effort.csv",sep=""))
```

## 3.4 Estimation
We shall estimate density of 'EPS' by 'MALIA' function
```{r}
tmp.Data<-Sight.Data %>%filter(type == "EPS")
res<-MALIA(tmp.Data,Effort.Data,key="hn",td=200)
```

Densities in each leg
```{r}
leg.D.plot(res$leg.D.obs$leg.result,xl=c(120,160),yl=c(20,50),save=F,Type="EPS")
```

## 3.5 Using full data 
SDAM function can conduct whole analysis
i.e) estimate detection function, calculate densities in each debris type, covariate and detection function
As it takes some time to finish all trials, we use already created results for mapping, model selection and making table.
```{r}
#res<-SDAM(Voyage.name=Vname,COVARIATE = c("conv", "occo","weather", "size"), key.list = c("hn","hr", "hhn", "hhr"),td=200,cp=10)
#Reading result object
res<-readRDS(paste(Vname,".result.obj",sep=""))
```

# 4. Result handling
## 4.1 Drawing maps
Maps with trackline and estimated density
```{r}
#let's see type 'EPS'
leg.D.res<-res$hhr$weather$EPS$leg.D.obs$leg.result
leg.D.plot(leg.D.res,save=F,Type='EPS')
```

Density of "EPS" by grid
```{r}
 grid.D.res<-res$hhr$weather$EPS$grid.D.res
 grid.D.plot(grid.D.res,save=F,Type='EPS')
```

## 4.2 Model selection
model summary
```{r}
 aic.mat<-aic.summary(res)
 aic.mat$EPS
```

model.extract function can extract best models in each debris type easily from SDAM result
```{r}
 best.model<-model.extract(aic.mat,res) 
 best.model$best.mat
```

## 4.3 Creating table
Summary of densities by leg
```{r}
 leg.table<-leg.D.table(best.model$best.list)
 head(leg.table)
 #write.xlsx(leg.table,file=paste(table.pass,"leg.D.table.xlsx",sep=""),row.names=F)
```
 
Summary of densities by grid
```{r}
 grid.table<-grid.D.table(best.model$best.list)
 head(grid.table)
 #write.xlsx(grid.table,file=paste(table.pass,"grid.D.table.xlsx",sep=""),row.names=F)
```

Summary of densities by area
```{r}
 area.table<-area.D.table(best.model$best.list)
 head(area.table)
 #write.xlsx(area.table,file=paste(table.pass,"area.D.table.xlsx",sep=""),row.names=F)
```

# 5. Ar and Nt products
## 5.1 Classify each debris into categories
ls. function can sum up artificial and natural products
```{r}
 Ar<-c("FGN","FGF","FGO","EPS","PBA","PBO","FP","PC","G","M","W","UO")
 Nt<-c("SW","DW","NO")
 An.table<-ls.(leg.table,Voyage.name,Ar,Nt)
 head(An.table)
```

Plot of Artificial product
```{r}
 Artificial.leg<-An.table %>%  select(Leg.No.,Leg.Length,Lat.Start,Lon.Start,Lat.End,Lon.End,Artificial_Density) %>% rename(Density=Artificial_Density)
 leg.D.plot(Artificial.leg,save=F)
 Artificial.grid<-grid.D(Artificial.leg)
 grid.D.plot(Artificial.grid,save = F)
```
 
Plot of Natural product
```{r}
Natural.leg<-An.table %>%  select(Leg.No.,Leg.Length,Lat.Start,Lon.Start,Lat.End,Lon.End,Natural_Density) %>% rename(Density=Natural_Density)
 leg.D.plot(Natural.leg,save=F)
 Natural.grid<-grid.D(Natural.leg)
 grid.D.plot(Natural.grid,save = F)
```

## 5.2 Combining results
Combining results across multiple surveys. In this procedure, it is necessary result objects has to already be created.
Survey legs
```{r}
 vname<-c("S18y4","O18y1","K18y1")
 tmp<-data.frame()
for(i in 1:length(vname)){
  Effort.Data<-read.csv(paste(vname[i],".effort.csv",sep=""))
  Effort.Data$voyage_name<-vname[i]
  tmp<-rbind(tmp,Effort.Data)
}
 survey.plot(tmp,multi=T)
```

Combine leg D results
In the leg.D.comb function, model selection and extraction of the best model are conducted.
```{r}
 tmp<-leg.D.comb(vname) 
#let's see type "DW"
 tmp2<-grid.D(tmp$DW)
 grid.D.plot(tmp2,save = F)
#area D
 tmp3<-area.D(tmp$DW)
 tmp3$area.density
```

Artificial and Natural products
Artificial product
```{r}
 tmp<-vanc(vname)
 leg.D.plot(tmp$Ar.leg.D,save=F)
 Artificial.grid<-grid.D(tmp$Ar.leg.D)
 grid.D.plot(Artificial.grid,save = F)
```

Natural product
```{r}
 leg.D.plot(tmp$Nt.leg.D,save=F)
 Natural.grid<-grid.D(tmp$Nt.leg.D)
 grid.D.plot(Natural.grid,save = F)
```

